Software

### 2025-04-24 software.qmd
update software

>>>>

## `impala`
I'm a devloper of the `impala` R package ([GitHub](https://github.com/sandialabs/rImpala)).

R library for modular Bayesian model calibration. Posterior exploration includes tempering and adaptive MCMC. This is an R tranlastion of the python library [impala](https://github.com/lanl/impala) by LANL
